---
title: "Interactive Maps"
output: html_document
---

```{r setup, include=FALSE}
library(leaflet)
library(raster)
library(RColorBrewer)

## Emissions and Temperature Maps {.tabset}

### Temperature

Interactive visualization of land surface temperature across Saudi Arabia (2018–2021).

```{r temperature-map}
leaflet() %>% ...



# Load temperature rasters
tem18 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/tem18.tif")
tem19 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/tem19.tif")
tem20 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/tem20.tif")
tem21 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/tem21.tif")

# Create a unified color scale
all_temp_vals <- c(values(tem18), values(tem19), values(tem20), values(tem21))
pal_temp <- colorNumeric(palette = "RdYlBu", domain = all_temp_vals, reverse = TRUE)

leaflet() %>%
  addTiles() %>%
  addRasterImage(tem18, colors = pal_temp, opacity = 0.7, group = "2018") %>%
  addRasterImage(tem19, colors = pal_temp, opacity = 0.7, group = "2019") %>%
  addRasterImage(tem20, colors = pal_temp, opacity = 0.7, group = "2020") %>%
  addRasterImage(tem21, colors = pal_temp, opacity = 0.7, group = "2021") %>%
  addLegend(pal = pal_temp, values = all_temp_vals, title = "Temperature (°C)") %>%
  addLayersControl(
    baseGroups = c("2018", "2019", "2020", "2021"),
    options = layersControlOptions(collapsed = FALSE)
  )


### CO₂

Carbon dioxide concentration patterns across Saudi cities from 2018 to 2021.

# Load CO₂ rasters
co2_2018 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/co218.tif")
co2_2019 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/co219.tif")
co2_2020 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/co220.tif")
co2_2021 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/co221.tif")

# Color scale
all_co2_vals <- c(values(co2_2018), values(co2_2019), values(co2_2020), values(co2_2021))
pal_co2 <- colorNumeric(palette = "YlOrRd", domain = all_co2_vals)

leaflet() %>%
  addTiles() %>%
  addRasterImage(co2_2018, colors = pal_co2, opacity = 0.7, group = "2018") %>%
  addRasterImage(co2_2019, colors = pal_co2, opacity = 0.7, group = "2019") %>%
  addRasterImage(co2_2020, colors = pal_co2, opacity = 0.7, group = "2020") %>%
  addRasterImage(co2_2021, colors = pal_co2, opacity = 0.7, group = "2021") %>%
  addLegend(pal = pal_co2, values = all_co2_vals, title = "CO₂ (ppm)") %>%
  addLayersControl(
    baseGroups = c("2018", "2019", "2020", "2021"),
    options = layersControlOptions(collapsed = FALSE)
  )


### CH₄

Methane distribution across Saudi Arabia (2018–2021), showing urban and agricultural sources.

# Load CH₄ rasters
ch4_2018 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/ch418.tif")
ch4_2019 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/ch419.tif")
ch4_2020 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/ch420.tif")
ch4_2021 <- raster("/Users/raghadaltassan/Library/Containers/com.apple.mail/Data/tmp/com.apple.mail.SavedAttachment-T0x600000881b80.tmp.Wtvzd4/senior project/data/ch421.tif")

# Color scale
all_ch4_vals <- c(values(ch4_2018), values(ch4_2019), values(ch4_2020), values(ch4_2021))
pal_ch4 <- colorNumeric(palette = "BuPu", domain = all_ch4_vals)

leaflet() %>%
  addTiles() %>%
  addRasterImage(ch4_2018, colors = pal_ch4, opacity = 0.7, group = "2018") %>%
  addRasterImage(ch4_2019, colors = pal_ch4, opacity = 0.7, group = "2019") %>%
  addRasterImage(ch4_2020, colors = pal_ch4, opacity = 0.7, group = "2020") %>%
  addRasterImage(ch4_2021, colors = pal_ch4, opacity = 0.7, group = "2021") %>%
  addLegend(pal = pal_ch4, values = all_ch4_vals, title = "CH₄ (ppb)") %>%
  addLayersControl(
    baseGroups = c("2018", "2019", "2020", "2021"),
    options = layersControlOptions(collapsed = FALSE)
  )

